### 2022-03-24 paper2.tex
review of ch 1

\hypertarget{paper-2}{%
\chapter{Information-Seeking Behaviors for Information on COVID-19 Vaccinations}\label{paper-2}}

@@

Previous research has greatly failed to distinguish between the activation of
information-seeking behaviors online and offline. Using theories of 1) social
support and 2) uses and gratifications theory I investigate the factors associated
with each modality type when on information-seeking modality: personal connection,
doctor, social networking site, online forum, and online search engine. Using
novel survey data of 948 Americans and their experience seeking out
information about the COVID-19 vaccines, I find little evidence that online
search is more utilized than seeking social support from personal network
connections or health professionals. I find evidence that the modalities queried
in this survey are conceptually different and that the utilization of different
modalities varies by demography and information sources. Finally, I find that
different sources of information exposure and information search modalities hold real
world consequences through their associations with COVID-19 vaccination rates
and intentions, as information from a doctor increased the COVID-19 vaccination
uptake while receiving information from a social networking site like Facebook
or Twitter was associated with lower odds of vaccination.

\textbf{Keywords}: Information-Seeking Behavior, COVID-19, Vaccine Hesitancy, Social Networks, Social Support, Information \& Communication Technologies

@@

I use the case of information around COVID-19 vaccinations to explore the
variation of usage of information search modalities. In doing so, I seek to answer
how computer-mediated or interpersonal information-seeking strategies vary
across populations in their search for information about COVID-19 vaccinations
and investigate how these strategies affect vaccination uptake. Specifically, this article 
answers two research questions: (1) How do computer-mediated or interpersonal information-seeking
strategies vary across populations? (2) How does the information search modality utilized 
affect COVID-19 Vaccination uptake?

Before addressing the results to these research questions, I offer an overview of the
current state of social science literature in regards to information-seeking
strategies and providing a description of the research methodology and
analytic sample. I then discuss the implications of these findings for the
sociological understanding of information search and vaccination uptake.

@@

There are important factors that can influence information-seeking strategies
besides the strength of social capital or ease of search. For instance, we can
borrow uses and gratifications theory (UGT) from studies of mass communication
\citep{blumlerUsesMassCommunications1974, tanMassCommunicationTheories1985}. 
UGT posits that users are not passive consumers of media and that people have an
active role in choosing different sources of media based on their satisfaction
of specific needs on an individual basis. UGT is based on Maslow’s  
\citeyear{maslowTheoryHumanMotivation1943} hierarchy of needs and is compatible with
Lazarsfeld and Katz’s theory of two-step flow \cite{katzPersonalInfluencePart1955}
because people can choose their media and the opinion leaders they follow.
Modern-day theorists have extended UGT theory and classified the uses and
gratifications of the internet and of social media. 
\citet{staffordDeterminingUsesGratifications2004} theorize that the internet
provides gratification through useful content that meets expectations,
gratification from purposeful navigating or random browsing as a process, and
social gratification from forming and deepening social ties. 
\citet{leungGenerationalDifferencesContent2013} theorizes that social media is
gratifying for users because it allows for venting of negative feelings,
provides recognition, provides entertainment, promotes social affection, and
fulfills cognitive needs.

@@

@@

The survey took an average of 24.48 minutes with a standard deviation of 13.23 minutes.
The shortest valid survey took 3.75 minutes and the longest took 111.08 minutes.
Participants received \$6.00 in compensation for their participation in the survey
\footnote{All funding for this survey was provided by a Grant awarded to Kelsey E. 
Gonzalez and Nicolas Legewie by the Summer Institute in Computational Social Science
and the Russell Sage Foundation.}. The survey consisted of two main parts. The
first portion of the survey is a replication of they survey conducted by 
\citet{smallSomeoneTalk2017}. In this section, we expand Small's research on 
support activation by segregating weak-tie social support into instrumental, 
emotional, and informational categories \citep[see][]{houseStructuresProcessesSocial1988}.
The second part of the survey focuses on network resource activation and 
information-seeking behaviors of individuals regarding COVID-19 vaccinations
for this paper.

@@

My analytic strategy proceeds in four steps. In Tables \ref{tab:table-1-ind}
\& \ref{tab:table-2-dep}, I present descriptive statistics for all study
variables, including variable ranges, means, and standard deviations. For this
paper, I rely heavily on logistic regression, modeled in \texttt{r}; specifically, I
fit a series of binomial generalized linear models with a logit link \citep{venables2002a},
otherwise known as logistic regression model \citep{hothorn2006handbook}.
This approach is appropriate because the data
are non-nested, cross-sectional data with binary independent variables. In Table \ref{tab:table-model-1}
\footnote{All Tables in this paper were created with the modelsummary package in \texttt{r} 
\citep{modelsummary}},I fit a logistic regression model predicting
whether someone sought information about COVID-19 using their sources of
information (`Received info') as well as various demographic variables such as
age, education level and race. Figure \ref{fig:plot-model-1} then illustrates
the relationship between the coefficients and information-seeking.\footnote{Figures 
in this paper were all created using the \texttt{r} packages jtools \citep{jtools}
and ggplot2 \citep{wickham_etal, wickham11}}.
In Table \ref{tab:model-2-phi}, I disaggregate information-seeking behaviors by
investigating the difference in proportions of each of the 5 different avenues
of seeking information about COVID-19: from another person, from a doctor, on an
online forum, on a social networking site, or using an online search tool. I
investigate these differences through a phi coefficient \citep{warrens08}, otherwise
known as a mean square contingency coefficient, which is used to investigate the
degree of association between two binary variables.\footnote{To calculate the Phi
  Coefficient, I utilize the Psych \texttt{r} package \citep{psych}} I then investigate the
associations between my predictors and the five information search modalities by
modelling a series of logistic regressions in Table \ref{tab:table-model-2}.
Finally, in Table \ref{tab:table-model-3}, I investigate whether there is a
relationship between information exposure sources, information-seeking behaviors and
the choice to get vaccinated against COVID-19 through a logistic regression
model predicting Vaccination Outlook. Figure \ref{fig:plot-model-3} then
illustrates the relationship between the coefficients and vaccination outlook.

@@

\hypertarget{information-seeking}{%
\subsection{information-seeking}\label{information-seeking}}

@@

Table \ref{tab:table-model-1} provides the results of my logistic regression
analysis predicting whether someone sought information about COVID-19. These
initial results suggest similar results for each modality of information
delivery: each mode of receiving information whether from a doctor, a person,
the news, a social networking site, or an online forum, all increase the odds of
seeking out information. For example, respondents who had received information
from a doctor or other medical professional were 2.82 (odds ratio = \(exp(\beta k)\),
\emph{p} \textless{} 0.001) times more likely to seek out information over someone
who had not. Similarly, respondents who had received information from `a
person like friend, neighbor, or family member that [they] know' were 1.87
(\emph{p} \textless{} 0.001) times more likely to seek out information over 
someone who had not received information from a person like that. Interesting, 
those who had received information from an online discussion group, listserv,
or other online forum including a Facebook group or subreddit were 2.39 (\emph{p}
\textless{} 0.001) times more likely to search out more information than 
someone who had not. While most demographic variables do not seem to have a 
strong effect on whether someone sought out information about the COVID-19 
vaccine, a few key variables had strong associations.  Respondents who are 
older are more likely to seek information; The odds are about 3\% higher when 
age is equal to x + 1 relative to x, possibly indicating a generational effect
of information-seeking patterns (\emph{p} \textless{} 0.01). Additionally,
those who were more educated, that is those with an Associate's degree or higher,
were 1.58 more likely to seek additional information than those without the degree
(\emph{p} \textless{} 0.05). And finally, there is evidence to suggest that the Black or
African American sample was more likely to seek out information, specifically:
Blacks were 3.58 times more likely to seek out information over non-Blacks (\emph{p}
\textless{} 0.05). Figure \ref{fig:plot-model-1} illustrates the relationship
between the coefficients and information-seeking.

@@

To further investigate how people search for information, I asked those who had
sought information out intentionally, ``How did you look for information about
the COVID-19 vaccine?'' Because respondents could select as many responses as
applicable, each response is recorded as a dichotomous variable. Table
\ref{tab:table-1-ind} reveals differences in the prevalence of usage of the
various information-seeking modalities: Around 40\% of the sample has inquired for
information from a doctor, a person, or using online search tool (44\%, 42\%, 41\%), while my
respondents used modalities like online forums (27\%) and social networking sites (18\%)
to seek out information at significantly lower rates.

@@

Finally, in Table \ref{tab:table-model-3}, I investigate whether there is a
relationship between information receiving and information-seeking behaviors and
the choice to get vaccinated against COVID-19 through a logistic regression
model predicting Vaccination Outlook. I find that receiving information from a
doctor or other medical profession is associated with 2.85 odds of choosing
to receive a COVID-19 vaccination (\emph{p} \textless{} 0.001) and that seeking 
information from a doctor also increases the odds of vaccination by 4 (\emph{p} \textless{} 0.001).
I find that my respondents who received information on a social networking site
like Facebook or Twitter about the vaccines were 55\%
\textbf{less likely} to choose to get vaccinated than those who received no information through
that modality (\emph{p} \textless{} 0.001). However, I did find that those who reached out to
family or friends with their concerns were 77\% more likely to become vaccinated 
(\emph{p} \textless{} 0.05). Furthermore, my respondents who held an Associate's degree
or above had 3.6 higher odds of becoming immunized (\emph{p} \textless{} 0.001).
And finally, I found further ethnoracial differences in my sample. I found that
Hispanic-Latinos had 2.83 higher odds of vaccination than non-Hispanics
(\emph{p} \textless{} 0.05) and that my Asian sample had 4.73 higher odds as well over
non-Asians (\emph{p}  = 0.09). See Figure \ref{fig:plot-model-3} for a visual
representation of how these different coefficients are related to vaccination outlook.

@@

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

Previous research in Sociology and Infodemiology has greatly failed to
distinguish between the activation of information-seeking behaviors online and
offline. In this paper, I sought to uncover just how different various methods of
information search are and begin a line of research inquiry that investigates
the factors associated with each different modality. Finally, I also uncovered
how the different sources of information exposure and information search
modalities hold real world consequences through their associations with COVID-19
vaccination rates and intentions.

@@

Table \ref{tab:table-model-2} further demonstrated important takeaways about
how individuals seek information. First, I find that the different information
seeking modalities queried in this survey are conceptually different and that the
utilization of different varies by demographic and information exposure source. 
Overall, being exposed to information about COVID-19 vaccinations from any 
source is associated with information-seeking behaviors,
though there are key variations. First, if one received information from a
doctor, they were likely to search from information from a doctor; this may
indicate an already existing trusting relationship between patient and
healthcare provider but it may also indicate the healthcare provider taking
initiative and emphasizing the importance of the vaccine or the survey respondent
seeking out information from an expert. Another important finding is that if you
received information from a social networking site like Facebook or Twitter, you
were less likely to query Online Forums like Reddit or Facebook Groups; this may
be an example of Uses and Gratification Theory
\citep{blumlerUsesMassCommunications1974}, where the two online platforms may act as
substitute sources of information and those who were satisfied with the
information they received on a social networking site didn't have the need to
seek out more information. Finally, the ethnoracial variations exhibited in
Table \ref{tab:table-model-2} likely demonstrate how cultural attitudes around
the trustworthiness of different sources of information affect the utilization
of different methods; for example, Asians seem are less likely to use online
forums than non-Asians, while Hispanics are more likely to use them than
non-Hispanics. The internal variations between the different information search
modalities hint at different user profiles and may have major repercussions on the
quality of information they find and who is exposed to poor quality information.

@@

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

Previous research has greatly failed to distinguish between the activation of
information-seeking behaviors online and offline and largely focuses on the
information that is sent to consumers [push], seeing people as passive receivers
of information. In this paper, I instead focus on individuals as active agents
in their search for information to begin a line of research inquiry that
investigates the factors associated with the various methods of information
search.

>>>>

\hypertarget{paper-2}{%
\chapter{information seeking Behaviors for Information on COVID-19 Vaccinations}\label{paper-2}}

@@

Previous research has greatly failed to distinguish between the activation of
information seeking behaviors online and offline. Using theories of 1) social
support and 2) uses and gratifications theory I investigate the factors associated
with each modality type when on information seeking modality: personal connection,
doctor, social networking site, online forum, and online search engine. Using
novel survey data of 948 Americans and their experience seeking out
information about the COVID-19 vaccines, I find little evidence that online
search is more utilized than seeking social support from personal network
connections or health professionals. I find evidence that the modalities queried
in this survey are conceptually different and that the utilization of different
modalities varies by demography and information sources. Finally, I find that
different sources of information exposure and information search modalities hold real
world consequences through their associations with COVID-19 vaccination rates
and intentions, as information from a doctor increased the COVID-19 vaccination
uptake while receiving information from a social networking site like Facebook
or Twitter was associated with lower odds of vaccination.

\textbf{Keywords}: information seeking Behavior, COVID-19, Vaccine Hesitancy, Social Networks, Social Support, Information \& Communication Technologies

@@

I use the case of information around COVID-19 vaccinations to explore the
variation of usage of information search modalities. In doing so, I seek to answer
how computer-mediated or interpersonal information seeking strategies vary
across populations in their search for information about COVID-19 vaccinations
and investigate how these strategies affect vaccination uptake. Specifically, this article 
answers two research questions: (1) How do computer-mediated or interpersonal information seeking
strategies vary across populations? (2) How does the information search modality utilized 
affect COVID-19 Vaccination uptake?

Before addressing the results to these research questions, I offer an overview of the
current state of social science literature in regards to information seeking
strategies and providing a description of the research methodology and
analytic sample. I then discuss the implications of these findings for the
sociological understanding of information search and vaccination uptake.

@@

There are important factors that can influence information seeking strategies
besides the strength of social capital or ease of search. For instance, we can
borrow uses and gratifications theory (UGT) from studies of mass communication
\citep{blumlerUsesMassCommunications1974, tanMassCommunicationTheories1985}. 
UGT posits that users are not passive consumers of media and that people have an
active role in choosing different sources of media based on their satisfaction
of specific needs on an individual basis. UGT is based on Maslow’s  
\citeyear{maslowTheoryHumanMotivation1943} hierarchy of needs and is compatible with
Lazarsfeld and Katz’s theory of two-step flow \cite{katzPersonalInfluencePart1955}
because people can choose their media and the opinion leaders they follow.
Modern-day theorists have extended UGT theory and classified the uses and
gratifications of the internet and of social media. 
\citet{staffordDeterminingUsesGratifications2004} theorize that the internet
provides gratification through useful content that meets expectations,
gratification from purposeful navigating or random browsing as a process, and
social gratification from forming and deepening social ties. 
\citet{leungGenerationalDifferencesContent2013} theorizes that social media is
gratifying for users because it allows for venting of negative feelings,
provides recognition, provides entertainment, promotes social affection, and
fulfills cognitive needs.

@@

% this actually makes more sense not from UGT but as a transactional cost perspective (maybe like disposable ties), that you have to use social capital to activate your social network, but online search is free.

@@

The survey took an average of 24.48 minutes with a standard deviation of 13.23 minutes.
The shortest valid survey took 3.75 minutes and the longest took 111.08 minutes.
Participants received \$6.00 in compensation for their participation in the survey
\footnote{All funding for this survey was provided by a Grant awarded to Kelsey E. 
Gonzalez and Nicolas Legewie by the Summer Institute in Computational Social Science
and the Russell Sage Foundation.}. The survey consisted of two main parts. The
first portion of the survey is a replication of they survey conducted by 
\citet{smallSomeoneTalk2017}. In this section, we expand Small's research on 
support activation by segregating weak-tie social support into instrumental, 
emotional, and informational categories \citep[see][]{houseStructuresProcessesSocial1988}.
The second part of the survey focuses on network resource activation and 
information seeking behaviors of individuals regarding COVID-19 vaccinations
for this paper.

@@

My analytic strategy proceeds in four steps. In Tables \ref{tab:table-1-ind}
\& \ref{tab:table-2-dep}, I present descriptive statistics for all study
variables, including variable ranges, means, and standard deviations. For this
paper, I rely heavily on logistic regression, modeled in \texttt{r}; specifically, I
fit a series of binomial generalized linear models with a logit link \citep{venables2002a},
otherwise known as logistic regression model \citep{hothorn2006handbook}.
This approach is appropriate because the data
are non-nested, cross-sectional data with binary independent variables. In Table \ref{tab:table-model-1}
\footnote{All Tables in this paper were created with the modelsummary package in \texttt{r} 
\citep{modelsummary}},I fit a logistic regression model predicting
whether someone sought information about COVID-19 using their sources of
information (`Received info') as well as various demographic variables such as
age, education level and race. Figure \ref{fig:plot-model-1} then illustrates
the relationship between the coefficients and information seeking.\footnote{Figures 
in this paper were all created using the \texttt{r} packages jtools \citep{jtools}
and ggplot2 \citep{wickham_etal, wickham11}}.
In Table \ref{tab:model-2-phi}, I disaggregate information seeking behaviors by
investigating the difference in proportions of each of the 5 different avenues
of seeking information about COVID-19: from another person, from a doctor, on an
online forum, on a social networking site, or using an online search tool. I
investigate these differences through a phi coefficient \citep{warrens08}, otherwise
known as a mean square contingency coefficient, which is used to investigate the
degree of association between two binary variables.\footnote{To calculate the Phi
  Coefficient, I utilize the Psych \texttt{r} package \citep{psych}} I then investigate the
associations between my predictors and the five information search modalities by
modelling a series of logistic regressions in Table \ref{tab:table-model-2}.
Finally, in Table \ref{tab:table-model-3}, I investigate whether there is a
relationship between information exposure sources, information seeking behaviors and
the choice to get vaccinated against COVID-19 through a logistic regression
model predicting Vaccination Outlook. Figure \ref{fig:plot-model-3} then
illustrates the relationship between the coefficients and vaccination outlook.

@@

\hypertarget{information seeking}{%
\subsection{Information Seeking}\label{information seeking}}

@@

Table \ref{tab:table-model-1} provides the results of my logistic regression
analysis predicting whether someone sought information about COVID-19. These
initial results suggest similar results for each modality of information
delivery: each mode of receiving information whether from a doctor, a person,
the news, a social networking site, or an online forum, all increase the odds of
seeking out information. For example, respondents who had received information
from a doctor or other medical professional were 2.82 (odds ratio = \(exp(\beta k)\),
\emph{p} \textless{} 0.001) times more likely to seek out information over someone
who had not. Similarly, respondents who had received information from `a
person like friend, neighbor, or family member that [they] know' were 1.87
(\emph{p} \textless{} 0.001) times more likely to seek out information over 
someone who had not received information from a person like that. Interesting, 
those who had received information from an online discussion group, listserv,
or other online forum including a Facebook group or subreddit were 2.39 (\emph{p}
\textless{} 0.001) times more likely to search out more information than 
someone who had not. While most demographic variables do not seem to have a 
strong effect on whether someone sought out information about the COVID-19 
vaccine, a few key variables had strong associations.  Respondents who are 
older are more likely to seek information; The odds are about 3\% higher when 
age is equal to x + 1 relative to x, possibly indicating a generational effect
of information seeking patterns (\emph{p} \textless{} 0.01). Additionally,
those who were more educated, that is those with an Associate's degree or higher,
were 1.58 more likely to seek additional information than those without the degree
(\emph{p} \textless{} 0.05). And finally, there is evidence to suggest that the Black or
African American sample was more likely to seek out information, specifically:
Blacks were 3.58 times more likely to seek out information over non-Blacks (\emph{p}
\textless{} 0.05). Figure \ref{fig:plot-model-1} illustrates the relationship
between the coefficients and information seeking.

@@

To further investigate how people search for information, I asked those who had
sought information out intentionally, ``How did you look for information about
the COVID-19 vaccine?'' Because respondents could select as many responses as
applicable, each response is recorded as a dichotomous variable. Table
\ref{tab:table-1-ind} reveals differences in the prevalence of usage of the
various information seeking modalities: Around 40\% of the sample has inquired for
information from a doctor, a person, or using online search tool (44\%, 42\%, 41\%), while my
respondents used modalities like online forums (27\%) and social networking sites (18\%)
to seek out information at significantly lower rates.

@@

Finally, in Table \ref{tab:table-model-3}, I investigate whether there is a
relationship between information receiving and information seeking behaviors and
the choice to get vaccinated against COVID-19 through a logistic regression
model predicting Vaccination Outlook. I find that receiving information from a
doctor or other medical profession is associated with 2.85 odds of choosing
to receive a COVID-19 vaccination (\emph{p} \textless{} 0.001) and that seeking 
information from a doctor also increases the odds of vaccination by 4 (\emph{p} \textless{} 0.001).
I find that my respondents who received information on a social networking site
like Facebook or Twitter about the vaccines were 55\%
\textbf{less likely} to choose to get vaccinated than those who received no information through
that modality (\emph{p} \textless{} 0.001). However, I did find that those who reached out to
family or friends with their concerns were 77\% more likely to become vaccinated 
(\emph{p} \textless{} 0.05). Furthermore, my respondents who held an Associate's degree
or above had 3.6 higher odds of becoming immunized (\emph{p} \textless{} 0.001).
And finally, I found further ethnoracial differences in my sample. I found that
Hispanic-Latinos had 2.83 higher odds of vaccination than non-Hispanics
(\emph{p} \textless{} 0.05) and that my Asian sample had 4.73 higher odds as well over
non-Asians (\emph{p}  = 0.09). See Figure \ref{fig:plot-model-3} for a visual
representation of how these different coefficients are related to vaccination outlook.

@@

\hypertarget{discussion}{%
\section{Discussion and Conclusion}\label{discussion}}

Previous research in Sociology and Infodemiology has greatly failed to
distinguish between the activation of information seeking behaviors online and
offline. In this paper, I sought to uncover just how different various methods of
information search are and begin a line of research inquiry that investigates
the factors associated with each different modality. Finally, I also uncovered
how the different sources of information exposure and information search
modalities hold real world consequences through their associations with COVID-19
vaccination rates and intentions.

% TODO explain finding about online search being less prominent than social networks, though opposite to the theory. relate this to Rains work and how it may be the search for personalized or experiential information making the difference.

@@

Table \ref{tab:table-model-2} further demonstrated important takeaways about
how individuals seek information. First, I find that the different information
seeking modalities queried in this survey are conceptually different and that the
utilization of different varies by demographic and information exposure source. 
Overall, being exposed to information about COVID-19 vaccinations from any 
source is associated with information seeking behaviors,
though there are key variations. First, if one received information from a
doctor, they were likely to search from information from a doctor; this may
indicate an already existing trusting relationship between patient and
healthcare provider but it may also indicate the healthcare provider taking
initiative and emphasizing the importance of the vaccine or the survey respondent
seeking out information from an expert. Another important finding is that if you
received information from a social networking site like Facebook or Twitter, you
were less likely to query Online Forums like Reddit or Facebook Groups; this may
be an example of Uses and Gratification Theory
\citep{blumlerUsesMassCommunications1974}, where the two online platforms may act as
substitute sources of information and those who were satisfied with the
information they received on a social networking site didn't have the need to
seek out more information. Finally, the ethnoracial variations exhibited in
Table \ref{tab:table-model-2} likely demonstrate how cultural attitudes around
the trustworthiness of different sources of information affect the utilization
of different methods; for example, Asians seem are less likely to use online
forums than non-Asians, while Hispanics are more likely to use them than
non-Hispanics. The internal variations between the different information search
modalities hint at different user profiles and may have major repercussions on the
quality of information they find and who is exposed to poor quality information.

@@

Previous research has greatly failed to distinguish between the activation of
information seeking behaviors online and offline and largely focuses on the
information that is sent to consumers [push], seeing people as passive receivers
of information. In this paper, I instead focus on individuals as active agents
in their search for information to begin a line of research inquiry that
investigates the factors associated with the various methods of information
search.

### 2022-03-24 paper3.tex
review of ch 1

To operationalize the search for online norms, I use Google search trends
\citep{googletrends}. In \hyperlink{paper-1}{\subsection{Article 1}}, I show
that Google Search Trends can only be used to indicate interest due to their low
criterion validity \citep{jungherr_etal17}. I use Google Trends over the study
period across individual designated media markets areas (DMAs), a nonoverlapping
aggregation of U.S. counties to 210 media markets based on similar population
clusters \citep{dma_key}. To investigate the rate of \emph{searching} for norms
online in both cases, I use the following search topics: `Social Distancing'
(2020, stay-at-home case only), `COVID-19 Vaccine' (2021, vaccination uptake
case only) and Covid Conspiracy (2020-2021, both cases). Search topics are a
more robust measurement than a single search term: topics are aggregations of
the rates of multiple, highly correlated search terms together into a cohesive
topic. For example, while `Beyoncé,' `Beyonce' and `beyonce knowles' are all
separate search terms, `Beyoncé Knowles' encompasses all of these into a single
search topic. While the data is originally on a scale of 0 to 100, with 100
being the maximum search popularity out of all DMAs, Google Search Trend are now
only available cross-sectionally (a single time period across a geography) or
time-series (a single geo-location across time). To remedy this and build a
longitudinal dataset of each search topic, I follow the method proposed in
\citet[p. 5]{park_etal}. This method involves building a dataset of unscaled
cross-sectional values, selecting a DMA to use to establish the rescaling ratio
(I use `Los Angeles CA'), and then finding the time-series values for the one
DMA. To find the rescaling ratio for each week in the time-series, you divide
the time-series value for each week by the cross-sectional value for each week,
resulting in a rescaling vector to be used for all weeks in the dataset across
geographies. To rescale each longitudinal value, multiply the respective week's
rescaling ratio by the cross-sectional value. Rescaled longitudinal data was
compared against time-series data for multiple test counties and was equivalent.
For a more in-depth explanation of this procedure, see \citet[p. 5]{park_etal}.

>>>>

To operationalize the search for online norms, I use Google search trends
\citep{googletrends}. In \hyperlink{paper-1}{Article 1}, I show
that Google Search Trends can only be used to indicate interest due to their low
criterion validity \citep{jungherr_etal17}. I use Google Trends over the study
period across individual designated media markets areas (DMAs), a nonoverlapping
aggregation of U.S. counties to 210 media markets based on similar population
clusters \citep{dma_key}. To investigate the rate of \emph{searching} for norms
online in both cases, I use the following search topics: `Social Distancing'
(2020, stay-at-home case only), `COVID-19 Vaccine' (2021, vaccination uptake
case only) and Covid Conspiracy (2020-2021, both cases). Search topics are a
more robust measurement than a single search term: topics are aggregations of
the rates of multiple, highly correlated search terms together into a cohesive
topic. For example, while `Beyoncé,' `Beyonce' and `beyonce knowles' are all
separate search terms, `Beyoncé Knowles' encompasses all of these into a single
search topic. While the data is originally on a scale of 0 to 100, with 100
being the maximum search popularity out of all DMAs, Google Search Trend are now
only available cross-sectionally (a single time period across a geography) or
time-series (a single geo-location across time). To remedy this and build a
longitudinal dataset of each search topic, I follow the method proposed in
\citet[p. 5]{park_etal}. This method involves building a dataset of unscaled
cross-sectional values, selecting a DMA to use to establish the rescaling ratio
(I use `Los Angeles CA'), and then finding the time-series values for the one
DMA. To find the rescaling ratio for each week in the time-series, you divide
the time-series value for each week by the cross-sectional value for each week,
resulting in a rescaling vector to be used for all weeks in the dataset across
geographies. To rescale each longitudinal value, multiply the respective week's
rescaling ratio by the cross-sectional value. Rescaled longitudinal data was
compared against time-series data for multiple test counties and was equivalent.
For a more in-depth explanation of this procedure, see \citet[p. 5]{park_etal}.
